Natural Stories

### 2020-06-08 Analysis/nat_stories.Rmd
checked how long comp question took to answer (involved redoing how compq data was arranged)

---
title: "Natural Stories"
output: github_document
---
```{r, include=F}
knitr::opts_chunk$set(echo = FALSE, warning=F)
options(knitr.table.format = "html")
library(tidyverse)
library(readr)
library(brms)
library(lme4)
library(rstan)
library(tidybayes)
library(knitr)
library(viridis)
library(cowplot)
theme_set(theme_bw())
rstan_options(auto_write = TRUE)
options(mc.cores = parallel::detectCores())
```

@@

data_error_summ <- data_filt %>% 
  mutate(correct.num=ifelse(correct=="yes", 1,0)) %>% 
  group_by(subject, critical, practice) %>%
  filter(type!="practice") %>% 
  filter(rt<5000) %>% 
  summarize(mean_rt=mean(rt),
            pct_correct=mean(correct.num)) %>% 
  mutate(critical_factor=as.character(critical*6),
         good_comp=ifelse(critical>.8,"5 or 6 correct","4 or fewer correct"))

ggplot(data_error_summ, aes(x=pct_correct, y=mean_rt, color=critical_factor))+
  geom_point()+
  facet_grid(.~good_comp)+
  labs(title="Relationship between error rate, RT, and comp ? accuracy",
       x="Percent maze correct",
       y="Mean reaction time",
       color="?s correct")

@@

for_plot <- data_error_summ %>% 
  mutate(num_correct=case_when(
    critical_factor %in% c("1","2","3") ~ "3 or fewer",
    T ~ critical_factor)) %>% 
    mutate(accurate=ifelse(pct_correct>.8,">80% correct", "<80% correct"))

ggplot(for_plot, aes(x=pct_correct, y=mean_rt, color=accurate))+
  geom_point(size=1)+
  scale_color_viridis(discrete=T)+
  labs(x="Fraction words selected correctly",
       y="Mean Reaction Time (ms)",
       color="?s correct")+
  coord_cartesian(xlim=c(0.4,1), ylim=c(0,1600))+
    scale_color_manual(values=c(">80% correct"="darkgreen","<80% correct"="darkred"))+
  guides(color=FALSE)

@@

some <- data_filt %>% select(subject, critical) %>% 
  unique() %>% 
  left_join(data_error_summ, by=c("subject", "critical")) %>% 
  mutate(accurate=ifelse(pct_correct>.8,">80% correct", "<80% correct")) %>% 
  mutate(correct=critical*6) %>% 
  group_by(correct,accurate)

ggplot(some, aes(x=correct,fill=accurate))+
  geom_bar(position="dodge")+
  facet_grid(.~accurate)+
  labs(x="Comp. questions correct (out of 6)", y="Participants")+
  scale_fill_manual(values=c(">80% correct"="darkgreen","<80% correct"="darkred"))+
guides(fill=FALSE)

@@

b <- cor(some$pct_correct, some$correct)

@@

@@

total_time <- data_filt %>% 
  mutate(correct.num=ifelse(correct=="yes", 1,0)) %>% 
  group_by(subject, critical, practice) %>%
  summarize(total_rt=sum(total_rt)/60000,
            pct_correct=mean(correct.num)) %>% 
  mutate(critical_factor=as.character(critical*6),
         good_comp=ifelse(critical>.8,"5 or 6 correct","4 or fewer correct"))

ggplot(total_time, aes(x=pct_correct, y=total_rt, color=critical_factor))+
  geom_point()+
  facet_grid(.~good_comp)+
  labs(title="How long does this take",
       x="Percent maze correct",
       y="Total maze time",
       color="?s correct")

@@

all <- data_filt %>% select(subject, critical) %>% 
  unique() %>% 
  mutate(correct=critical*6) %>% 
   group_by(correct) %>% 
  tally() %>% 
  mutate(pct=n/95) %>% 
  mutate(source="all Maze") %>% 
  select(source,correct, pct)

some <- data_filt %>% select(subject, critical) %>% 
  unique() %>% 
  left_join(data_error_summ, by=c("subject", "critical")) %>% 
  filter(pct_correct>.8) %>% 
  mutate(correct=critical*6) %>% 
   group_by(correct) %>% 
  tally() %>% 
  mutate(pct=n/63) %>% 
  mutate(source="Maze >80% correct") %>% 
  select(source,correct, pct)

@@

c <- data_filt %>% filter(type!=practice) %>%
  group_by(subject, sentence) %>%
  mutate(is.error=ifelse(correct=="no",1,0)) %>%
  summarize(mistakes=sum(is.error)) %>%
  mutate(no_mistake=ifelse(mistakes==0,"Error-free","Errorful")) %>%
  select(subject, sentence, no_mistake) %>%
  left_join(for_plot, by="subject")

@@

```{r exclusion}
data_good <- data_filt %>% 
  left_join(data_error_summ, by=c("subject", "critical")) %>% 
  filter(type!="practice") %>% 
  filter(pct_correct>.8) %>% 
  mutate(is.correct=ifelse(correct=="yes",1,0))

>>>>

---
title: "Natural Stories"
output: github_document
---
```{r, include=F}
knitr::opts_chunk$set(echo = FALSE, warning=F)
options(knitr.table.format = "html")
library(tidyverse)
library(readr)
library(brms)
library(lme4)
library(rstan)
library(tidybayes)
library(knitr)
library(cowplot)
theme_set(theme_bw())
rstan_options(auto_write = TRUE)
options(mc.cores = parallel::detectCores())
```

@@

data_error_summ <- data_filt %>% 
  mutate(correct.num=ifelse(correct=="yes", 1,0)) %>% 
  group_by(subject, num_correct) %>%
  filter(type!="practice") %>% 
  filter(rt<5000) %>% 
  summarize(mean_rt=mean(rt),
            pct_correct=mean(correct.num)) %>% 
  mutate(good_comp=ifelse(num_correct>4,"5 or 6 correct","4 or fewer correct"))

ggplot(data_error_summ, aes(x=pct_correct, y=mean_rt, color=as.factor(num_correct)))+
  geom_point()+
  facet_grid(.~good_comp)+
  labs(title="Relationship between error rate, RT, and comp ? accuracy",
       x="Percent maze correct",
       y="Mean reaction time",
       color="?s correct")

@@

for_plot <- data_error_summ %>% 
  # mutate(num_correct=case_when(
  #   critical_factor %in% c("1","2","3") ~ "3 or fewer",
  #   T ~ critical_factor)) %>% 
    mutate(accurate=ifelse(pct_correct>.8,">80% correct", "<80% correct"))

ggplot(for_plot, aes(x=pct_correct, y=mean_rt, color=accurate))+
  geom_point(size=1)+
  labs(x="Fraction words selected correctly",
       y="Mean Reaction Time (ms)",
       color="?s correct")+
  coord_cartesian(xlim=c(0.4,1), ylim=c(0,1600))+
    scale_color_manual(values=c(">80% correct"="darkgreen","<80% correct"="darkred"))+
  guides(color=FALSE)

@@

ggplot(for_plot, aes(x=pct_correct, y=mean_rt))+
  geom_point()+
  labs(x="Fraction words selected correctly",
       y="Mean Reaction Time (ms)",
       color="?s correct")+
  coord_cartesian(xlim=c(0.4,1), ylim=c(0,1600))+
    #scale_color_manual(values=c(">80% correct"="darkgreen","<80% correct"="darkred"))+
  guides(color=FALSE)

ggsave("../error.jpg", width=5, height=3, unit="in")

some <- data_filt %>% select(subject, num_correct) %>% 
  unique() %>% 
  left_join(data_error_summ, by=c("subject", "num_correct")) %>% 
  mutate(accurate=ifelse(pct_correct>.8,">80% correct", "<80% correct")) %>% 
  group_by(num_correct,accurate)

ggplot(some, aes(x=num_correct,fill=accurate))+
  geom_bar(position="dodge")+
  facet_grid(.~accurate)+
  labs(x="Comp. questions correct (out of 6)", y="Participants")+
  scale_fill_manual(values=c(">80% correct"="darkgreen","<80% correct"="darkred"))+
guides(fill=FALSE)

@@

@@

## Are comprehension questions working

As was raised when I presented this at lab meeting, it could be that participants are looking up answers to comprehension questions, so we want to check based on length.

correct <- data_filt %>% select(subject, num_correct, correct_answer_1:correct_answer_6) %>% unique() %>% 
  pivot_longer(correct_answer_1:correct_answer_6, names_to=c("q_num"), values_to=c("is.correct"), names_prefix="correct_answer_")

time <- data_filt %>% select(subject, num_correct, q_time_1:q_time_6) %>% unique() %>% 
  pivot_longer(q_time_1:q_time_6, names_to=c("q_num"), values_to=c("q_time"), names_prefix="q_time_") %>% 
  left_join(correct, by=c("subject", "num_correct","q_num")) %>% 
  left_join(data_error_summ, by=c("subject","num_correct")) %>% 
      mutate(accurate=ifelse(pct_correct>.8,">80% correct", "<80% correct")) %>% 
  filter(q_time<20000)

ggplot(time, aes(x=q_time))+geom_density()+facet_grid(.~accurate)

time_filt <- time %>%  filter(q_time<10000) %>% 
  group_by(subject, accurate) %>% summarize(mod_pct_correct=sum(is.correct), mean_pct_correct=mean(is.correct))

ggplot(time_filt, aes(x=mod_pct_correct))+geom_histogram()+facet_grid(.~accurate)
```

Can play around with cutoffs etc, but the net result is that most of the answering is happening within 10 (much within 5) seconds, and it doesn't look like people are looking up answers, so comprehension is probably reliable.

@@

total_time <- data_filt %>% 
  mutate(correct.num=ifelse(correct=="yes", 1,0)) %>% 
  group_by(subject, num_correct) %>%
  summarize(total_rt=sum(total_rt)/60000,
            pct_correct=mean(correct.num)) %>% 
  mutate(         good_comp=ifelse(num_correct>4,"5 or 6 correct","4 or fewer correct"))

ggplot(total_time, aes(x=pct_correct, y=total_rt, color=as.factor(num_correct)))+
  geom_point()+
  facet_grid(.~good_comp)+
  labs(title="How long does this take",
       x="Percent maze correct",
       y="Total maze time",
       color="?s correct")

@@

all <- data_filt %>% select(subject, num_correct) %>% 
  unique() %>% 
  mutate(correct=num_correct) %>% 
   group_by(correct) %>% 
  tally() %>% 
  mutate(pct=n/95) %>% 
  mutate(source="all Maze") %>% 
  select(source,correct, pct)

some <- data_filt %>% select(subject, num_correct) %>% 
  unique() %>% 
  left_join(data_error_summ, by=c("subject", "num_correct")) %>% 
  filter(pct_correct>.8) %>% 
  mutate(correct=num_correct) %>% 
   group_by(correct) %>% 
  tally() %>% 
  mutate(pct=n/63) %>% 
  mutate(source="Maze >80% correct") %>% 
  select(source,correct, pct)

@@

c <- data_filt %>% filter(type!="practice") %>%
  group_by(subject, sentence) %>%
  mutate(is.error=ifelse(correct=="no",1,0)) %>%
  summarize(mistakes=sum(is.error)) %>%
  mutate(no_mistake=ifelse(mistakes==0,"Error-free","Errorful")) %>%
  select(subject, sentence, no_mistake) %>%
  left_join(for_plot, by="subject")

@@

```{r exclusion}
data_good <- data_filt %>% 
  left_join(data_error_summ, by=c("subject", "num_correct")) %>% 
  filter(type!="practice") %>% 
  filter(pct_correct>.8) %>% 
  mutate(is.correct=ifelse(correct=="yes",1,0))
